\myTitle

### 2024-10-30 tex/body-text-of-paper.tex
changes from overleaf

This marker set and baseline reference dataset provide
unprecedented power for identifying fish from all of the Chinook salmon ESUs in California,
as well as individual populations within those ESUs (Fig.~\ref{fig:gsi}).
Accurate identification of the distinct ecotypes of Chinook salmon in the
California Central Valley is of utmost importance for designing and implementing
effective conservation and management actions. The CCV is one of the largest river
basins on the west coast of North America and has the highest diversity of recognized Chinook salmon
ecotypes in the species range, with four named ecotypes, two of which are protected
under the US Endangered Species Act. This basin drains the Sierra Nevada and southern Cascade
mountain ranges and is the source of water for several major urban areas as well as the
largest and most valuable agriculture area in North America. As such, monitoring and
evaluation of individual ecotypes and populations is of critical importance. This has been challenging,
given the recent common ancestors of these ecotypes \citep{clemento2014evaluation}, and
ongoing migration between subbasins where different ecotypes predominate.

>>>>

This marker set and baseline reference dataset provide
unprecedented power for identifying fish from all of the Chinook salmon ESUs in California,
as well as individual populations within those ESUs (Fig.~\ref{fig:gsi}).
The California Central Valley (CCV) is one of the largest river
basins on the west coast of North America and drains the Sierra Nevada and southern Cascade
mountain ranges. It has the highest diversity of recognized Chinook salmon
ecotypes in the species range, with four named ecotypes, two of which are protected
under the US Endangered Species Act. It is also the source of water for several major urban areas as well as the
largest and most valuable agriculture area in North America. As such, accurate identification of the distinct ecotypes of CCV Chinook salmon is of utmost importance for monitoring and
evaluation of individual ecotypes, as well as designing and implementing
effective conservation and management actions. This has been challenging,
given the recent common ancestors of these ecotypes \citep{clemento2014evaluation}, and
ongoing migration between subbasins where different ecotypes predominate.
